Insert title of project here

### 2022-03-29 Draft Report/Draft Project.Rmd
added working directory, change as you wish

```{r setup, include=FALSE}
# Set your working directory

# Load your packages
library(agricolae)
library(corrplot)
library(cowplot)
library(dataRetrieval)
library(extrafont)
library(extrafontdb)
library(ggpubr)
library(ggthemes)
library(hrbrthemes)
library(Kendall)
library(leaflet)
library(lubridate)
library(mapview)
library(rvest)
library(sf)
library(tidycensus)
library(tidyverse)
library(trend)
library(tseries)
library(viridis)
library(zoo)

>>>>

```{r, initialize}
# Set your working directory
getwd()
knitr::opts_knit$set(root.dir = "~/Desktop/Duke MPP/Environ Data /Environmental_Data_Analytics_2022/")

```{r setup, include=FALSE}
# Load your packages
library(agricolae)
library(corrplot)
library(cowplot)
library(dataRetrieval)
library(extrafont)
library(extrafontdb)
library(ggpubr)
library(ggthemes)
library(hrbrthemes)
library(Kendall)
library(leaflet)
library(lubridate)
library(mapview)
library(rvest)
library(sf)
library(tidycensus)
library(tidyverse)
library(trend)
library(tseries)
library(viridis)
library(zoo)
